\documentclass[a4paper,12pt]{article}
\usepackage{url}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
	language=C++,
	aboveskip=3mm,
	belowskip=3mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\small\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	stringstyle=\color{mauve},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3
}
\begin{document}
	
	\title{CS-224 Object Oriented Programming and Design Methodologies }
	\author{Assignment 05}
	\date{October 15, 2018}
	\maketitle
	\section{Guidelines}
	You need to submit this assignment on  {\color{red}26th of October at 630 pm } as the next assignment will be given on the same day. Some important guidelines about the assignment are as following:
	
	\begin{itemize}
		\item You need to do all the assignments alone
		\item You will submit your assignment to git-hub 
		\item You need to follow the best programming practices 
		\item Submit assignment on time; late submissions will not be accepted.
		\item Some assignments will require you to submit multiple files. Always Zip and send them.
		\item It is better to submit incomplete assignment than none at all.
		\item It is better to submit the work that you have done yourself than what you have plagiarized.
		\item It is strongly advised that you start working on the assignment the day you get it. Assignments WILL take time.
		\item Every assignment you submit should be a single zipped file containing all the other files. Suppose your name is John Doe and your id is 0022 so the name of the submitted file should be JohnDoe0022.zip
		\item DO NOT send your assignment to your instructor, if you do I will just mark your assignment as ZERO for not following clear instructions.
		\item You can be called in for Viva for any assignment that you submit
	\end{itemize}
	
	\section{Task}
	For this assignment you are given the file \path{SmartString.h} that contains the sample code. The tasks you need to accomplish are:\smallskip\\
	
	\begin{itemize}
		\item You will need to implement all the functions of the SmartString class exactly like they have been declared in the header file.
		\item  You cannot change the access specifiers of either the attributes or the functions.
		\item You cannot add extra attributes to the class itself. The functions can have local variables.
		\item Try to use functions inside one another to maximize code reuse.
		\item You will need to define \path{SmartString.cpp} and \path{main.cpp}
		\item All the functions of the SmartString class must work in the main file
		\item This is the last programming assignment, so do not forget to treat yourself once it is done!
	\end{itemize}
	
	\begin{center}
		-- The End --
	\end{center}
	\newpage
	
	
\end{document}